% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={BHLnames},
  pdfauthor={John Doe, Jane Doe},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=2cm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\hypersetup{colorlinks=false, allbordercolors={0.6 0.6 1}, pdfborderstyle={/S/U/W 0.5}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{BHLnames}
\author{John Doe, Jane Doe}
\date{2021-10-27}

\begin{document}
\maketitle

\begin{itemize}
\tightlist
\item
  \protect\hyperlink{abstract}{Abstract}

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{background}{Background}
  \item
    \protect\hyperlink{new-information}{New information}
  \end{itemize}
\item
  \protect\hyperlink{keywords}{Keywords}
\item
  \protect\hyperlink{classifications}{Classifications}

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{taxon-classification}{Taxon Classification}
  \item
    \protect\hyperlink{subject-classification}{Subject classification}
  \end{itemize}
\item
  \protect\hyperlink{funder}{Funder}
\item
  \protect\hyperlink{introduction}{Introduction}
\item
  \protect\hyperlink{project-description}{Project description}

  \begin{itemize}
  \tightlist
  \item
    \protect\hyperlink{goals}{Goals}
  \item
    \protect\hyperlink{technical-introduction}{Technical introduction}
  \item
    \protect\hyperlink{architecture}{Architecture}

    \begin{itemize}
    \tightlist
    \item
      \protect\hyperlink{dependencies}{Dependencies}
    \end{itemize}
  \item
    \protect\hyperlink{workflow}{Workflow}

    \begin{itemize}
    \tightlist
    \item
      \protect\hyperlink{preprocessed-data-for-naive-bayes-classifier}{Preprocessed
      data for Naive Bayes classifier}
    \item
      \protect\hyperlink{initialization-and-data-import}{Initialization
      and data import}
    \item
      \protect\hyperlink{configuration-file-creation}{Configuration file
      creation}
    \item
      \protect\hyperlink{database-and-cache-initialization}{Database and
      cache initialization}

      \begin{itemize}
      \tightlist
      \item
        \protect\hyperlink{year-processing}{Year processing}
      \item
        \protect\hyperlink{page-and-volume-number-processing}{Page and
        volume number processing}
      \item
        \protect\hyperlink{scientific-names-processing}{Scientific names
        processing}
      \item
        \protect\hyperlink{calculation-of-a-taxonomic-statistic}{Calculation
        of a taxonomic statistic}
      \item
        \protect\hyperlink{normalization-of-the-books-and-journals-titles}{Normalization
        of the books' and journals' titles}
      \item
        \protect\hyperlink{nomenclatural-annotations}{Nomenclatural
        annotations}
      \end{itemize}
    \item
      \protect\hyperlink{main-functionality}{Main functionality}

      \begin{itemize}
      \tightlist
      \item
        \protect\hyperlink{taxonomic-intelligence-workflow}{Taxonomic
        intelligence workflow}
      \item
        \protect\hyperlink{nomenclatural-references-workflow}{Nomenclatural
        references workflow.}

        \begin{itemize}
        \tightlist
        \item
          \protect\hyperlink{collecting-evidences-of-a-citation-match}{Collecting
          ``evidences'' of a citation match}
        \item
          \protect\hyperlink{making-a-decision}{Making a decision}
        \end{itemize}
      \item
        \protect\hyperlink{arbitrary-references-workflow}{Arbitrary
        references workflow}
      \end{itemize}
    \item
      \protect\hyperlink{finding}{Finding}
    \end{itemize}
  \item
    \protect\hyperlink{interfaces}{Interfaces}

    \begin{itemize}
    \tightlist
    \item
      \protect\hyperlink{input-formats}{Input formats}
    \item
      \protect\hyperlink{gui}{GUI}

      \begin{itemize}
      \tightlist
      \item
        \protect\hyperlink{embeddable-widget}{Embeddable widget}
      \item
        \protect\hyperlink{api}{API}
      \item
        \protect\hyperlink{command-line}{Command line}
      \end{itemize}
    \end{itemize}
  \item
    \protect\hyperlink{audience}{Audience}

    \begin{itemize}
    \tightlist
    \item
      \protect\hyperlink{examples-of-usages}{Examples of usages}
    \item
      \protect\hyperlink{summary-of-scores}{Summary of scores}
    \item
      \protect\hyperlink{benchmarks}{Benchmarks}
    \item
      \protect\hyperlink{open-data-deliverables}{Open data deliverables}
    \end{itemize}
  \item
    \protect\hyperlink{conclusions}{Conclusions}
  \end{itemize}
\item
  \protect\hyperlink{web-location-uris}{Web location (URIs)}
\item
  \protect\hyperlink{technical-specification}{Technical specification}
\item
  \protect\hyperlink{repository}{Repository}
\item
  \protect\hyperlink{usage-license}{Usage license}
\item
  \protect\hyperlink{implementation}{Implementation}
\item
  \protect\hyperlink{additional-information}{Additional information}
\item
  \protect\hyperlink{acknowledgements}{Acknowledgements}
\item
  \protect\hyperlink{author-contributions}{Author contributions}
\item
  \protect\hyperlink{references}{References}
\item
  \protect\hyperlink{figures}{Figures}
\item
  \protect\hyperlink{tables}{Tables}
\item
  \protect\hyperlink{supplementary-material}{Supplementary material}
\item
  \protect\hyperlink{endnotes}{Endnotes}
\end{itemize}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{background}{%
\subsection{Background}\label{background}}

\begin{itemize}
\tightlist
\item
  BHL exists
\item
  CoL exists
\item
  Global Names exists
\item
  BHL has index
\item
  COL has names with nomenclatural publications
\end{itemize}

\hypertarget{new-information}{%
\subsection{New information}\label{new-information}}

\begin{itemize}
\tightlist
\item
  BHlnames now exists
\item
  BHLnames solves these 3 problems
\item
  Can access via web
\item
  Can access via API
\item
  Can see name-\textgreater description via file
\item
  Local use is possible
\end{itemize}

\hypertarget{keywords}{%
\section{Keywords}\label{keywords}}

biodiversity informatics, biodiversity heritage library, catalogue of
life, global names, nomenclature, taxonomy, library informatics

\hypertarget{classifications}{%
\section{Classifications}\label{classifications}}

\hypertarget{taxon-classification}{%
\subsection{Taxon Classification}\label{taxon-classification}}

? Animalia, Plantae, all other from the list

\hypertarget{subject-classification}{%
\subsection{Subject classification}\label{subject-classification}}

Bioinformatics

\hypertarget{funder}{%
\section{Funder}\label{funder}}

Species File Group, BHL index

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Over the past 268 years, an estimated 2.5 million species have been
named, described, and published in scientific journals by taxonomists
around the world using the Linnaean classification system (Linnaeus
1753). In order to describe new species it is imperative that
taxonomists are able to quickly find and access past species
descriptions to avoid re-describing an existing species with a new
scientific name, and to hypothesize on how the new species is related to
other species based on morphology and other characteristics. The field
of biodiversity informatics is still relatively young and there is still
a huge backlog of work remaining to digitize past scientific literature,
index the scientific names, and parse other unstructured scientific data
from hundreds of years of past literature into a form that will be more
usable for conducting research (Le Guillarme and Thuiller 2021).

Historically there has been a disconnect between the disciplines of
biology and library science with different subdisciplines of taxonomy
developing nomenclature and citation styles independently of one another
and using non-standardized abbreviations that suited the specific needs
of their subdisciplines, and librarians implementing metadata policies
without conversing enough with biologists, resulting in suboptimal
information systems that make it difficult and time consuming to
efficiently conduct taxonomic research (Pilsk et al. 2010). Building a
stronger collaboration between biologists, information scientists, and
library scientists could help improve the of findability, accessibility,
interoperability, and reusability (FAIR, (Wilkinson et al. 2016)) of
biodiversity knowledge which hopefully will help accelerate responding
to emerging crises from climate change and biodiversity decline (Urban
2015).

Biodiversity Heritage Library (BHL) is the largest open access
collection of biodiversity literature. BHL was founded in 2005 to
increase open access to biodiversity literature and is governed by an
international consortium (Gwinn and Rinaldo 2009, Rinaldo and Norton
2009, Smith and Rinaldo 2016, Kalfatovic et al. 2019). BHL currently
comprises of 270 thousand volumes and 60 million pages of biodiversity
texts. Perhaps the most common way to discover biodiversity information
in BHL is by searching for scientific names of biological organisms.

The search index of scientific names for BHL was developed and is
maintained by the Global Names Architecture (GNA) project (Costantino
2020, Richard 2020). GNA was founded in 2007 with the aim of providing
services and tools that globally connect biodiversity information and
research via scientific names. GNA includes nomenclatural (ZooBank, a
zoological names registrar (Krell and Pyle 2010, Patterson et al. 2010,
Pyle 2016)) and lexical tools (GNfinder, GNverifier, GNparser). The
GNfinder tool can be used to detect potential scientific names within
text documents by searching for text patterns that follow the Linnaean
nomenclature system (Linnaeus 1753). GNverifier enables searching for
scientific names in more than 100 sources of biodiversity data, which is
used to help verify if potential scientific names found by GNfinder in
text documents are actually scientific names. GNverifier uses data from
Catalogue of Life, Encyclopedia of Life, Index Fungorum, Global
Biodiversity Information Facility and many others. GNparser (Mozzherin
et al. 2017b) normalizes scientific names and extracts the semantic
meanings of each component (FIG, Mozzherin et al. (2017a)). Normalizing
scientific names also enables organizing lexical variants of a name into
a lexical group.

A scientific name search tool, BHLindex, was developed through a 10 year
collaboration between GNA and BHL (Mozzherin 2021). BHLindex breaks each
volume into tokenized words, which enables the heuristic and natural
language processing algorithms of GNfinder to detect potential
scientific names within a volume's text. Potential scientific names are
verified (reconciled and resolved) via GNverifier. The process of
generating the BHL scientific names index has been highly optimized for
performance, which enables processing 60 million BHL pages in
\textasciitilde12 hours on a modern laptop. The speed of the BHL index
creation offers the major advantage of being able to continuously
improve BHL search as the scanned page OCR improves (Mozzherin et al.
2017a, Herrmann 2020), and also allows incremental improvements to the
scientific name finding algorithms of GNA tools. GNverifier also
augments the metadata for each BHL volume by attempting to determine the
kingdom and lowest clade that contain the most scientific names within a
BHL volume using management classification from Catalogue of Life
(Gordon 2009).

The Catalogue of Life (CoL) project was established in 2000 with the
goal of developing a global species checklist of all currently accepted
scientific names (Reichhardt 1999, Bisby 2000, Wilson and Bisby 2007).
As of this writing, CoL contains over 2 million accepted species.
Searching in BHL for a biological organism using only its currently
accepted scientific name could exclude a significant amount of
information about the organism due to changes in taxon names over time.
CoL tracks historical scientific names that are no longer accepted and
contains 1.6 million of these synonyms. The database of GNverifier
contains 8 million scientific names, for \textasciitilde2.5 million
known taxa. From this data we estimate there are an average of 2 to 3
names per taxon, which fits with other published estimates (3.5
names/taxon in seed plants (Scotland and Wortley 2003), but synonymy can
vary by group with an estimate of only 1.2 names/taxon in stoneflies
(DeWalt and Ower 2019)). To obtain more comprehensive knowledge about a
biological organism, it is important to search not by just one
scientific name, but by all synonyms used in the literature for the
organism historically.

Another way to access information in BHL is by searching for a
particular paper. Thanks to the BioStor project, metadata and page
locations are known for \textasciitilde310,000 papers in BHL (Page 2010,
Page 2011). However, designing software to automatically link to any
paper in BHL by a citation string is still challenging. There are a
large variety of lexical variants for every journal name (FIG). No
standard for citation formatting was ever agreed upon by publishers, so
the arrangement of authors, year of publication, volume, issue, and page
widely varies. It is much easier to search for a year, volume and page
data as numbers, but in BHL numeric metadata is stored as a string and
is not consistently formatted throughout the corpus with many journals
in the past using Roman numerals. Quite often metadata is missing
entirely or contains errors, which complicates automatically linking
citation strings to the correct page in BHL. Of the 3.7 million
scientific names in CoL, 53\% have nomenclatural references to the
original species description in the literature, and BHLnames attempts to
automatically link to these citations in BHL.

TODO: Fig: examples of journal name different spellings

Even if a researcher has the citation for a nomenclatural event, it is
often not a trivial task to navigate to the exact page in BHL in order
to access the original species description for research. Citations are
hard to match to pages in BHL as described above. Sometimes OCR errors
change a name spelling and as a result exist in a volume under different
spelling variants.

Quite often people add an annotation next to new species or combination,
such as sp. nov., comb. nov. However such annotations are not consistent
(FIG), and also often modified by OCR. When several species of the same
genus are described, the genus in the name is often abbreviated, which
also masks the name from a researcher.

TODO: Fig: examples for annotations

The project we describe in this paper helps to adress these problems
with the following solutions: 1) BHLnames uses a combination of the
names index, CoL data, and BHL metadata to improve nomenclatural and
taxonomic search, link a citation string to a page in BHL, or link to
pages containing the original species description. 2) BHLnames
normalizes BHL data for publication years and pages, making it easier to
compare numeric representations. 3) The project uses 2,085,819 million
citations of nomenclatural events for names in CoL to provide data about
nomenclatural events. 4) BHLnames normalizes journal names in order to
match citation strings to the journal name in BHL. 5) We use a Naive
Bayes algorithm to calculate probabilities of a citation to BHL page
match and return the best results. The data linking CoL nomenclatural
citations to the original species description pages in BHL is
downloadable from the Dryad data repository (Link).

\hypertarget{project-description}{%
\section{Project description}\label{project-description}}

Title: BHLnames

Study area description: Biodiversity Informatics

Design description: This is the whole paper actually (?)

\hypertarget{goals}{%
\subsection{Goals}\label{goals}}

The goals of BHLnames project are to:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Add ``taxonomic intalligence'' to the BHL's index of scientific names.

  Supplement the nomenclatural event index with CoL synonym data to
  optionally extend BHL name search to include all relevent taxonomical
  information by returning search results for the accepted name and all
  of its synonyms.
\item
  Link to original species descriptions and nomenclatural events in BHL.

  Use citation search in combination with CoL nomenclatural citations to
  build an nomenclatural event index that will increase usability of BHL
  for biodiversity researchers.
\item
  Dramatically simplify citation string search using the names index.

  Use citation metadata in combination with occurences of a scientific
  name to link to pages that potentially match the citation with a
  provided probability score.
\end{enumerate}

(Methods)

\hypertarget{technical-introduction}{%
\subsection{Technical introduction}\label{technical-introduction}}

BHLnames an Open Source project written in Go and JavaScript. It can be
freely used by anyone with Internet connection, write access to a
PostgreSQL database, and XXX GB of disk space. It consists of one
stand-alone binary file and requires no additional dynamic libraries.
The file can be downloaded at:
https://github.com/gnames/bhlnames/releases Useage requires an
initialization stage that can take several hours to complete, but
afterwards the BHLnames binary can be used without an internet
connection.

\hypertarget{architecture}{%
\subsection{Architecture}\label{architecture}}

BHLnames' code structure mostly adheres to Clean Architecture principles
(Martin 2018). The main use-case functionality is defined in an
interface (Link?). The core (entity) modules that do not require
input/output (I/O) interactions with a database, the internet or local
storage, are located in the `ent' directory. The `ent' directory also
contains interfaces implemented by modules that need I/O access. The
Clean Architecture approach is advantageous because it uncouples core
modules from particular implementations of external I/O processes and
provides flexibility for changing ways of storing and accessing the
data. Modules requiring database, internet, user interfaces, or
framework accesss implement entity interfaces and depend on the main
use-case interface for providing functionality of BHLnames. One
exception to this rule is the `bhlnames' directory that contains the
commandline interface, following convention established by its Cobra
module dependency.

BHLnames provides 3 user interfaces:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The commandline application starts and stops the web service or
  provides BHLnames functionality via the terminal.
\item
  The RESTful API provides endpoints for remote access to BHLnames
  functionality via HTTP calls.
\item
  The web interface is a Javascript widget that can be embedded on any
  website to connect scientific names with BHL literature in an
  interactive pop-up modal.
\end{enumerate}

\hypertarget{dependencies}{%
\subsubsection{Dependencies}\label{dependencies}}

The project requires installed PostgreSQL database.

Initialization phase of the project requires internet access to a data
export from BHL (https://www.biodiversitylibrary.org/data/data.zip) and
the BHLindex RESTful API. Internet connection must be reasonably fast
due to the large amount of downloaded data.

BHLindex is an Open Source application written in Go that creates a
scientific names index of BHL. The application scans BHL's 60 million
pages, detects scientific names and provides data about their page
location via RESTful interface. It is possible to use publicly available
URL that serves BHLindex API at (LINK).

There are many dependencies on Go modules, some of them written
specifically for Global Names project. We will talk about some of GN
modules further. Go dependencies are required only during the
compilation of the project and are not needed for running BHLnames
service or commandline application.

\hypertarget{workflow}{%
\subsection{Workflow}\label{workflow}}

BHLnames has 2 distinct steps. Initialization and service.
Initialization step requires remote access to BHL data dumps and to a
RESTful API of BHLindex service. Service step provides a user with a
web-interface, RESTful API and comman-line application to get taxonomic
details about names, match nomenclatural reference to a page in BHL,
match a reference string to BHL pages.

\hypertarget{preprocessed-data-for-naive-bayes-classifier}{%
\subsubsection{Preprocessed data for Naive Bayes
classifier}\label{preprocessed-data-for-naive-bayes-classifier}}

In the program we use Naive Bayes algorithm for determining the most
like candidates for citation matching. This algorithm is based on
collection of evidences that make References in BHL more or less likely
candidates to a match with a citation. For this algorithm to function we
need to decide beforehand which evidences will be collected for each
case and how much weight each of them has to influence the final
decision.

To calculate such weights for all used types of evidence we manually
went through 3500 citation detection cases, and partitioned them into
correctly and incorrectly identified (REF). This data is saved into a
JSON file and is stored statically inside of the BHLnames binary
executable. The data allowed us to calculate weights for each of the
evidence type.

\hypertarget{initialization-and-data-import}{%
\subsubsection{Initialization and data
import}\label{initialization-and-data-import}}

From BHL's dumped files BHLnames receives metadata about Titles, Items,
Pages and Parts. BHL term Titles includes entities that might contain
one or more volumes, for example a book or a journal. Items correspond
to physical volumes; an Item can be a book, a volume of a journal etc.
Pages correspond to scanned and processed pages of an Item. Parts are
distinct entities inside of an Item. For example a scientific paper is a
Part. Metainformation from BHL allows to integrate scientific names
detected in BHL corpus to the rest of the data.

BHLindex API provides data and metadata about scientific names detected
in BHL corpus. Each name's occurence is associated with Internet Archive
identifiers for a volume and a page. Also it contains location on a
page, and results of verificaton process. Verification process resolves
the name, if possible to a taxonomic database, like Catalogue of Life,
or provides information if a name reconciles to a name in some other
resource registered for GNverifier service.

Reconciliation is a process of matching a name to its lexical variants.
Resolution allows to receive taxonomic information for a particular
name: if a names is a synonym, what is currently accepted name for the
taxon, what kind of classification is associated with the taxon.

\hypertarget{configuration-file-creation}{%
\subsubsection{Configuration file
creation}\label{configuration-file-creation}}

BHLnames requires an access to PostgreSQL database. Also it needs to
know where to find BHL datafiles and how to access BHLindex' RESTful
API. All this data has to be included into configuration file. The file
is created as \$HOME/.config/bhlnames.yaml when BHLnames commandliine
application is executed first time. A user has to edit the file and
enter database credentials. All other settings can be left at its
default values.

After that the application is ready for initialization.

\hypertarget{database-and-cache-initialization}{%
\subsubsection{Database and cache
initialization}\label{database-and-cache-initialization}}

To begin the process of initialization BHLnames has to create all the
tables for its PostgreSQL database and create its cache directory for
downloaded and processed data.

The database (default name is ``bhlnames'') should already exist (be
created by hand). It does not matter if it does have some data already
or if it is totallly empty. BHLnames initialization process will remove
all old data and create required tables from scratch. Now the database
is ready to import the new data.

The cache directory structure is located at the OS standard location. On
most Linux distributions it would be created at
``\$HOME/.cache/bhlnames''. In case if the directory exists already, old
data will be removed, so it will not be able to interfere with the
updated data.

Then the initialization step downloads all the relevant data from BHL
download site and from RESTful BHLindex API interface, processes it, and
saves the result into a relational PostgreSQL database.

From the BHL's downloaded data we use ``title.txt'', ``item.txt'',
``page.txt'', and ``part.txt'' files. The `title.txt' file contains
metainformation for Titles, for example journals or books. The
`item.txt' contains information about Items, for example a particular
volume of a journal or a book. The `page.txt' has metadata about pages
in an Item. The `part.txt' provides metadata about Parts of an Item, for
example about a scientific paper title, authors, start and end page etc.

During the import several data-fields require additional attention. Such
fields include data about years of publication, volume, page
information.Much of the data about detected name-strings will also be
processed. The largest processing job is required for the Titles'
titles, for example a title of a book, a name of a journal etc. We use
such titles extensively for the matching process, and they will be
prepared for fast matchins as it is described further.

\hypertarget{year-processing}{%
\paragraph{Year processing}\label{year-processing}}

There are several fields with year information in BHL metadata.

The ``titles'' have `StartYear' and `EndYear' fields corresponding to
beginning of a pubhlishing and the end of the publishing. The ``items''
have `Year' field corresponding to the date of publication. However, in
practice' some ``items'' might span several years, if they contain
volumes of a journal rebound together. The ``parts'' have a ``Date''
field, usually in a `yyyy-mm-dd' format where ``-mm'' and ``-dd'' parts
are optional.

The year of publication data can be extracted from all of these fields,
however some, or all of these fields might be empty. Is some rare
occastions the ``year fields'' are contradictory. To determine a year of
publicaton for a particular name we check for existence of a year
information going order ``part'', ``item'', ``title''. For example if we
found that the page is inside of a ``part'', we use the ``part's'' date
to determine a year. If ``title'' information is used, the ``EndYear''
value becomes a year for a page, indicating that the page could not be
published later than this year. For some pages no year data exists.

\hypertarget{page-and-volume-number-processing}{%
\paragraph{Page and volume number
processing}\label{page-and-volume-number-processing}}

Page number is an important field for connecting name occurance with the
publication metadata, however the ``PageNumber'' field in ``page.txt''
cannot always be easily converted to an integer. The value of the field
is not always numeric, to name a few:

\begin{verbatim}
(1966, v.15, No.15)
, fig. A-B
, p. 431-436
, xiii-xiv
18 (Tab. XXXVII, XXX
208, Fig. 3
\end{verbatim}

The page number is converted to an integer where possible.

The Volume information more often than not is not numeric; for example:

\begin{verbatim}
10, n. 20
Armitage, W.H.
v.2, pt. 1
(2020: Mar.)
0007
v.58:pt.1 (1889)
v.8:no.21 (2004:Apr)
\end{verbatim}

We store volume data as is, without conversion to an integer.

\hypertarget{scientific-names-processing}{%
\paragraph{Scientific names
processing}\label{scientific-names-processing}}

More often than not a scientific name appears more than once in a
volume. To decrease the amount of noise we check if a page where name is
found is included into a ``part'', for example a scientific paper. If
yes, only the first occurance of a name in the ``part'' is included. If
a name is also detected in an ``item'', for example a journal volume,
but is not part of any known ``part'', the first instance of a name in
an ``item'' is included. If there no ``parts'' are assigned to an
``item'', only the first appearance of a name in an ``item'' is
included.

Every name string that is reconciled to a name in the Catalogue of Life
(61.8\% of all verified names) is associated with taxonomic resolution
of a name-string to a clade in the Catalogue of Life. For example,
``Felis concolor'' name-string is associated with a species clade where
currently accepted name is ``Puma concolor'' according to the Catalogue
of Life.

\hypertarget{calculation-of-a-taxonomic-statistic}{%
\paragraph{Calculation of a taxonomic
statistic}\label{calculation-of-a-taxonomic-statistic}}

Having most of the name-strings reconciled to the Catalogue of Life
allows to calculate major kingdom and major clade appeared in BHL
``items''. All such names contain their placement in the managerial
Catalogue of Life classification. This placement allows us to find out
distribution of such names between kingdoms of the classification.

We are also able to find which clade in the classification contains more
than 50\% of all names resolved to the Catalogue of Life. To calculate
it, we find how the names are distributed over each of ``kingdom'',
``phylum/domain'', ``class'', ``order'', ``family''. Knowing the total
number of names for each clade, we calculate the percentage for each
clade, and pick one that contains more than 50\% of all such names. For
example a book about Wolf Spiders would have more than 50\% of all CoL
names in the order of ``Lycosidae''.

Taxonomic statistics allows to find out a biological ``theme'' for the
most of BHL volumes.

\hypertarget{normalization-of-the-books-and-journals-titles}{%
\paragraph{Normalization of the books' and journals'
titles}\label{normalization-of-the-books-and-journals-titles}}

BHL's ``title.txt'' contains a ``FullTitle'' field. This field contains
the full title of a journal or a book. Citations of scientific
publications almost always contain a title of a journal, so this field
is very useful for matching a citation and a BHL Title. However titles
in citations are usually abbreviated, and the same title can have a
large lexical variants where words are shortened or omitted in a hardly
predictable way. Fuzzy matching in this circumstances would be very
time-consuming and would produce unreliable results. Moreover,
citation's title is in the middle of other information and to extract it
as a separate entity is also very hard task.

For example, citation ``Kirschstein, W. In: Verh. bot. Ver. Prov.
Brandenb. 48:50. (1907).'' contains abbreviated title to ``Verhandlungen
des Botanischen Vereins für die Provinz Brandenburg.''. Taking in
account that citations often come from different sources and title
abbreviations are not standardised, matching the citation to the title
rarely succeeds. In this manuscript we tried a new apprach that seems to
be working quite well for matching a citation to a journal title.

We made two observations. First, that no matter how much a title is
shortened, the first letter of the words have a tendency to survive.
Second, some words tend to be discarded from a shortened version
alltogether. Like in the example below ``des'', ``für'' and ``die''
words are totally discared from the shortened version of a title ``Verh.
bot. Ver. Prov. Brandenb''.

We went through three thousand pairs of journal titles and their
abbreviated counterparts. We extracted words that are often get removed
from shortened titles (TODO link to
https://github.com/gnames/bhlnames/blob/master/io/dictio/data/excluded.txt).
Furthe we call these words ``excluded''.

Then we created 2 ``fingerprints'' for each title in BHL. First
``fingerprint'' contains the first letter of every word in a title. For
the second ``fingerprint'' we remove all ``exlcuded'' words from the
title and then take first letter of every word that left. For example
``Verhandlungen des Botanischen Vereins für die Provinz Brandenburg.''
would be normalized to ``vdbvfdpb'' and ``vbvpb'' fingerprints. The
reason we created two fingerprints is an obervation that more often than
not, the ``excluded'' words either stay in a citation intact, or are
removed from a citation completely.

For our example we end up with the following fingerprints:

\begin{verbatim}
The Journal Title:
Verhandlungen des Botanischen Vereins für die Provinz Brandenburg.
vdbvfdpb, vbvpb

The Citation:
Kirschstein, W. In: Verh. bot. Ver. Prov. Brandenb. 48:50. (1907).
kwivbvpb
kwvbvpb
\end{verbatim}

The second ``fingerprint'' from the journal title ``vbvpb'' is included
into the second ``fingerprint'' of the citation ``kw\textbf{vbvpb}''.
Therefore we can assume that the citation contains the title of the
journal.

Additional rules for fingerprint creatsion are:

\begin{itemize}
\tightlist
\item
  Journal titles with less than 3 words do not get ``fingerprints''
  created.
\item
  Word ``and'' and ``\&'' both become ``\&''.
\item
  The ``fingerprints'' longer than 10 characters are truncated to the
  first 10 characters.
\end{itemize}

During the data import we create approximately 400,000 ``fingerprints''
from BHL Titles titles. Understandably it would be very time consuming
to find which fingerprints out of these 400,000 are included into each
citation. Because of that we implemented an Aho-Corasick algorithm (REF,
REF) that allows very fast pattern inclusion detection via a
modification of a suffix tree approach.

All of the data generated for the Aho-Corasick algorithm during
initializationis backed up to the BHLnames' cache directory. When
BHLnames starts again this data is read and loaded into the memory
according to the Aho-Corasick algorithm. In then can be used for a very
fast queies that match citations to the titles recorded in BHL database.

\hypertarget{nomenclatural-annotations}{%
\paragraph{Nomenclatural annotations}\label{nomenclatural-annotations}}

When BHLindex detects scientific names in BHL corpus, it also detects
the presence of ``nomenclatural annotations'' in a vicinity of each name
occurence.

Nomenclatural annotions differ slightly depending on a year of
publication, exiting nomenclatural rules, and a personality of authors.
In addition optical character recognition omits or modifies some
characters. As a result we found a large variety of nomenclatural
annotations in BHL texts. Here are a few examples:

\begin{verbatim}
sp.nov
sp. nov."。
n, sp:
subsp nov.
ssp. nov.?
'sp. n.),
nov. comb)
n. sp;;
(nov. comb)
n. sp..»
sp. nov.'.
sp« n.
sp., 2n.),
|n. sp.].
nov. sp.(3),
n. sp.,375
n> sp>
nv. sp.
(n, sp,):
nv. sp.,
(sp?) n
(n. sp,?)
sp. nov,).
sp. (n=5).
sp. nov.228
subsp.' nov.,
,n. comb.;
sp. nov.557
n. sp.38
(n. comb,
nov. sp.121
^,sp. n.,
nov. subsp).
nov. sp.^)
\end{verbatim}

We normalized all the variants into the following categories:

\begin{verbatim}
SP_NOV    - new species
SUBSP_NOV - new subspecies
COMB_NOV  - new combination
NO_ANNOT  - no nomenclatural annotation
\end{verbatim}

\hypertarget{main-functionality}{%
\subsubsection{Main functionality}\label{main-functionality}}

The BHLnames program helps to find answers to these three questions:

\begin{itemize}
\tightlist
\item
  Where BHL contains information about a taxon, given a name string that
  can be resolved to the taxon.
\item
  Where is a page which corresponds to a given nomenclatural citation +
  a name-string.
\item
  Where is a BHL page which corresponds to a given reference + a
  name-string.
\end{itemize}

\hypertarget{taxonomic-intelligence-workflow}{%
\paragraph{Taxonomic intelligence
workflow}\label{taxonomic-intelligence-workflow}}

A ``taxonomic intelligence'' workflow includes an input and output. The
input consists of one or more scientific name-strings. The output
provides information which taxon the name resolves to, what is the
currently accepted name for the taxon according to the Catalogue of
Life, provides a link to images of the taxon according to Encyclopedia
of Life, describes sinonym names for the taxon. Also it tells how many
references include information about the taxon. Then it provides list of
references which include the taxon together with page links.

Every Reference also provides additional statistics about its Item. It
tells how many unique name-strings were detected in the Item, What is
the kindom that contains the majority of detected names, what is the
smallest taxon that contains more than half of all detected names.

Reference here can be a Part, or Item. If Item contains the name inside
of Parts and outside of any Part, data is provided for the first
detection of the taxon in each of these entities.

The main difference between this approach and search of BHL by name is
that the search aggregates information about all mentions of a taxon in
BHL, no matter what name associated with a taxon was detected. This
approach allows to get data linked from all literature in BHL, no matter
when it was published and independently on development of Taxonomic
science.

Optionally, it is possible to limit the list of returned references to a
particular name and avoid the expansion of search to all synonyms.

(TODO an example of output)

\hypertarget{nomenclatural-references-workflow.}{%
\paragraph{Nomenclatural references
workflow.}\label{nomenclatural-references-workflow.}}

Publications that contain nomenclatural events are especially valuable
for taxonomists. Such publications might contain description of new
species, changes in names of species as a result of placing them in a
different genus, changed rank, ``promotion'' of infraspecies to species
etc.

BHLnames makes it possible to discover such publicatons in BHL by
providing an input that consists of a name-string created in the
publivcation and the citation of the publication. It is helpful if such
details about publicaton like the year of publication, volume and page
numbers are given separately in their own fields.

(TODO Example of input in JSON)

\hypertarget{collecting-evidences-of-a-citation-match}{%
\subparagraph{Collecting ``evidences'' of a citation
match}\label{collecting-evidences-of-a-citation-match}}

To be able to estimate how sure we are that we did find the page where a
particular nomenclatural citation exists, we collect several pices of
``evidence'' that would provide as clues about validity of our
assurance.

In natural language processing such evidences are often called
``features'', and, as a rule, none of these evidences are an iron-clad
indicator of a success. We have to collect several types of them and use
calculated weights for each of the evidence to make the final judgement.
The Naive Bayes method assumes that all of these features have no
influence on each other. And while some rule do influence each other,
from the practical standpoint Naive Bayes classifiers work quite well in
many cases.

Now we will describe the evidences we collect to make a decision.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Name-string matching
\end{enumerate}

The first step after receiving an input is finding all the References
that contain a requested name. Such search is performed without
synonymy, so it only contains References that contain the name-string.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  BHL Title's title matching
\end{enumerate}

In the next step the titles of the References are compared with provided
citatons. We used descirbed earlier title ``fingerprints'' for a fast
matching of citations to the titles of BHL Titles (books, journals
etc.).

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Year matching
\end{enumerate}

The algorithm tries to match the year of the input citation with the
years of the found References. Note that sometimes the year of BHL
Reference is known only approximately, for example if there is only
Titile's start and end of publication data are given. Sometimes there is
no year information at all. The algorithm takes in account not only
exact matches of a year, but also cases where a Reference year is close
to the provided year in the input.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Page numers, volume matching
\end{enumerate}

We use heuristic algorithms to compare given year, volume, page numbers
information to match them to References obtained during the first step.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Nomenclatural annotations
\end{enumerate}

More often than not, papers describing new species would have a
nomenclatural annotation like ``sp. nov.'', ``comb. nov'' etc. We
normalized annotations occured in BHL as described earlier. If a name
occurance contains such annotation, it is registered as another
``evidendce'' in favor that the Reference is the nomenclatural one from
the citation.

\hypertarget{making-a-decision}{%
\subparagraph{Making a decision}\label{making-a-decision}}

Using precalculated weights for the described above ``evidences'' we
derive a total matching score for each Reference. After that we are able
to sort the references by the score and decide if the top result has a
score high enough for being classified as a possible occurance of the
citation in BHL.

The value of the score allows us to state a probabiliby of cussessful
citation detection in the BHL corpus.

\hypertarget{arbitrary-references-workflow}{%
\paragraph{Arbitrary references
workflow}\label{arbitrary-references-workflow}}

The workflow for finding of arbitrary refernces is quite similar to the
detetection of nomenclatural references. The input is identical, and
collection of ``evidences'', scoring and decision making are almost the
same. The only difference is that we do not take in account
nomenclatural annotations located in the vicinity of the name-string.

\hypertarget{finding}{%
\subsubsection{Finding}\label{finding}}

\hypertarget{interfaces}{%
\subsection{Interfaces}\label{interfaces}}

\hypertarget{input-formats}{%
\subsubsection{Input formats}\label{input-formats}}

\hypertarget{gui}{%
\subsubsection{GUI}\label{gui}}

\hypertarget{embeddable-widget}{%
\paragraph{Embeddable widget}\label{embeddable-widget}}

\hypertarget{api}{%
\paragraph{API}\label{api}}

\hypertarget{command-line}{%
\paragraph{Command line}\label{command-line}}

\hypertarget{audience}{%
\subsection{Audience}\label{audience}}

CoL ZooBank WoRMS? TW BHL users (Trei 2016) Taxonomists Librarians
Historians Citizen Scientists Nomenclators Artists Other Reseachers

(Results)

\hypertarget{examples-of-usages}{%
\subsubsection{Examples of usages}\label{examples-of-usages}}

\hypertarget{summary-of-scores}{%
\subsubsection{Summary of scores}\label{summary-of-scores}}

\hypertarget{benchmarks}{%
\subsubsection{Benchmarks}\label{benchmarks}}

\hypertarget{open-data-deliverables}{%
\subsubsection{Open data deliverables}\label{open-data-deliverables}}

(Discussion)

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

\begin{itemize}
\tightlist
\item
  Jigsaw puzzle where a name is the first piece.
\item
  We add more pieces
\end{itemize}

Advantages, impact

Missing parts

Ways to improve

How it helps for the other future developments

How to contribute?

Funding: skip it here? Same as above

\hypertarget{web-location-uris}{%
\section{Web location (URIs)}\label{web-location-uris}}

Homepage: bhlnames.globalnames.org

Wiki: github.com/gnames/bhlnames wiki (maybe, or nothing)

Download page: data or code? * code: https://github.com/gnames/bhlnames
* data: some place on Dryad?

Download mirror: n/a

Bug database: https://github.com/gnames/bhlnames/issues

Mailing list: https://gitter.io/gnames/something ?

Blog: http://globalnames.org

Vendor: N/A ask Matt

\hypertarget{technical-specification}{%
\section{Technical specification}\label{technical-specification}}

Platform: ?

Programming language: Go, JavaScript?

Operating system: GNU/Linux

Interface language: JavaScript?

Service endpoint: * https://bionames.globalnames.org/api/v1 *
https://apidoc.globalnames.org/bhlnames

\hypertarget{repository}{%
\section{Repository}\label{repository}}

Type: Git

Browse URI: https://github.com/gnames/bhlnames

Location: ?

Module: ?

Anonymous root: n/a

\hypertarget{usage-license}{%
\section{Usage license}\label{usage-license}}

MIT

\hypertarget{implementation}{%
\section{Implementation}\label{implementation}}

Implements specification: N/A

Audience:

\hypertarget{additional-information}{%
\section{Additional information}\label{additional-information}}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Thanks to you all. Rich Pyle for journal data

\hypertarget{author-contributions}{%
\section{Author contributions}\label{author-contributions}}

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{figures}{%
\section{Figures}\label{figures}}

\hypertarget{tables}{%
\section{Tables}\label{tables}}

\hypertarget{supplementary-material}{%
\section{Supplementary material}\label{supplementary-material}}

\hypertarget{endnotes}{%
\section*{Endnotes}\label{endnotes}}
\addcontentsline{toc}{section}{Endnotes}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Bisby2000}{}}%
Bisby FA (2000) {The quiet revolution: Biodiversity informatics and the
Internet}. Science 289: 2309--2312.
\url{https://doi.org/10.1126/science.289.5488.2309}

\leavevmode\vadjust pre{\hypertarget{ref-Costantino2020}{}}%
Costantino G (2020) {BHL Improves the Speed and Accuracy of its
Taxonomic Name Finding Services with gnfinder}. Available from:
\url{https://blog.biodiversitylibrary.org/2020/07/bhl-improvestaxonomic-name-services-gnfinder.html}.

\leavevmode\vadjust pre{\hypertarget{ref-DeWalt2019}{}}%
DeWalt RE, Ower GD (2019) Ecosystem services, global diversity, and rate
of stonefly species descriptions (insecta: plecoptera). 10.
\url{https://doi.org/10.3390/insects10040099}

\leavevmode\vadjust pre{\hypertarget{ref-Gordon2009}{}}%
Gordon DP (2009) {Towards a management hierarchy (classification) for
the Catalogue of Life: Draft Discussion Document}. Available from:
\url{https://web.archive.org/web/20090330224421/http://www.catalogueoflife.org/annual-checklist/2009/info\%7B/_\%7Dhierarchy.php}.

\leavevmode\vadjust pre{\hypertarget{ref-Gwinn2009}{}}%
Gwinn NE, Rinaldo C (2009) {The Biodiversity Heritage Library: Sharing
biodiversity literature with the world}. IFLA Journal 35: 25--34.
\url{https://doi.org/10.1177/0340035208102032}

\leavevmode\vadjust pre{\hypertarget{ref-Herrmann2020}{}}%
Herrmann E (2020) {Building the Biodiversity Heritage Library's
Technical Strategy}. Biodiversity Information Science and Standards 4.
\url{https://doi.org/10.3897/biss.4.59084}

\leavevmode\vadjust pre{\hypertarget{ref-Kalfatovic2019}{}}%
Kalfatovic MR, Costantino G, Rinaldo CA (2019) {The Biodiversity
Heritage Library: Unveiling a World of Knowledge About Life on Earth}.
In:, 352--355. \url{https://doi.org/10.1007/978-3-030-30760-8_32}

\leavevmode\vadjust pre{\hypertarget{ref-Krell2010}{}}%
Krell FT, Pyle RL (2010) {ZooBank progress report}. Bulletin of
Zoological Nomenclature 67: 271--277.

\leavevmode\vadjust pre{\hypertarget{ref-LeGuillarme2021}{}}%
Le Guillarme N, Thuiller W (2021) {TaxoNERD: Deep neural models for the
recognition of taxonomic entities in the ecological and evolutionary
literature}. Methods in Ecology and Evolution.
\url{https://doi.org/10.1111/2041-210X.13778}

\leavevmode\vadjust pre{\hypertarget{ref-Linnaeus1753}{}}%
Linnaeus C (1753) vol. 1 Species plantarum: Exhibentes plantas rite
cognitas, ad genera relatas, cum differentiis specificis, nominibus
trivialibus, synonymis selectis, locis natalibus, secundum systema
sexuale digestas. Stockholm: Impensis Laurentii Salvii.
\url{https://doi.org/10.5962/bhl.title.669}

\leavevmode\vadjust pre{\hypertarget{ref-Martin2018}{}}%
Martin RC (2018) Clean architecture: A craftsman's guide to software
structure and design. Prentice Hall. Available from:
\url{https://books.google.com/books?id=8ngAkAEACAAJ}.

\leavevmode\vadjust pre{\hypertarget{ref-Mozzherin2021}{}}%
Mozzherin D (2021) {Connecting Taxonomic Backbones using Global Names
Tools}. Biodiversity Information Science and Standards 5.
\url{https://doi.org/10.3897/biss.5.75619}

\leavevmode\vadjust pre{\hypertarget{ref-Mozzherin2017}{}}%
Mozzherin DY, Myltsev AA, Patterson DJ (2017a) {A path to continuous
reindexing of scientific names appearing in Biodiversity Heritage
Library data}. Proceedings of TDWG 1: e20186.
\url{https://doi.org/10.3897/tdwgproceedings.1.20186}

\leavevmode\vadjust pre{\hypertarget{ref-Mozzherin2017a}{}}%
Mozzherin DY, Myltsev AA, Patterson DJ (2017b) {"gnparser": a powerful
parser for scientific names based on Parsing Expression Grammar}. BMC
Bioinformatics 18: 279. \url{https://doi.org/10.1186/s12859-017-1663-3}

\leavevmode\vadjust pre{\hypertarget{ref-Page2010}{}}%
Page R (2010) {Finding scientific articles in a large digital archive:
BioStor and the Biodiversity Heritage Library}. Nature Precedings:
1--19. \url{https://doi.org/10.1038/npre.2010.4928.1}

\leavevmode\vadjust pre{\hypertarget{ref-Page2011}{}}%
Page RD (2011) {Extracting scientific articles from a large digital
archive: BioStor and the Biodiversity Heritage Library}. BMC
Bioinformatics 12: 187. \url{https://doi.org/10.1186/1471-2105-12-187}

\leavevmode\vadjust pre{\hypertarget{ref-Patterson2010}{}}%
Patterson DJ, Cooper J, Kirk PM, Pyle RL, Remsen DP (2010) {Names are
key to the big new biology}. Trends in Ecology and Evolution 25:
686--691. \url{https://doi.org/10.1016/j.tree.2010.09.004}

\leavevmode\vadjust pre{\hypertarget{ref-Pilsk2010}{}}%
Pilsk SC, Person MA, Deveer JM, Furfey JF, Kalfatovic MR (2010) {The
Biodiversity Heritage Library: Advancing Metadata Practices in a
Collaborative Digital Library}. Journal of Library Metadata 10:
136--155. \url{https://doi.org/10.1080/19386389.2010.506400}

\leavevmode\vadjust pre{\hypertarget{ref-Pyle2016}{}}%
Pyle RL (2016) {Towards a global names architecture: The future of
indexing scientific names}. ZooKeys 2016: 261--281.
\url{https://doi.org/10.3897/zookeys.550.10009}

\leavevmode\vadjust pre{\hypertarget{ref-Reichhardt1999}{}}%
Reichhardt T (1999) {Catalogue of life could become reality}. Nature
399: 519--519. \url{https://doi.org/10.1038/21051}

\leavevmode\vadjust pre{\hypertarget{ref-Richard2020}{}}%
Richard J (2020) {Improving Taxonomic Name Finding in the Biodiversity
Heritage Library}. Biodiversity Information Science and Standards 4.
\url{https://doi.org/10.3897/biss.4.58482}

\leavevmode\vadjust pre{\hypertarget{ref-Rinaldo2009}{}}%
Rinaldo C, Norton C (2009) {BHL, The Biodiversity Heritage Library: An
Expanding International Collaboration}. Nature Precedings.
\url{https://doi.org/10.1038/npre.2009.3620.1}

\leavevmode\vadjust pre{\hypertarget{ref-Scotland2003}{}}%
Scotland RW, Wortley AH (2003) {How many species of seed plants are
there?} Taxon 52: 101--104.

\leavevmode\vadjust pre{\hypertarget{ref-Smith2016}{}}%
Smith JE, Rinaldo CA (2016) {Collaborating on open science: The journey
of the Biodiversity Heritage Library}. Dobreva M, Schmidt B (Eds).
Information Services \& Use 35: 211--216.
\url{https://doi.org/10.3233/ISU-150785}

\leavevmode\vadjust pre{\hypertarget{ref-Trei2016}{}}%
Trei K (2016) {The Biodiversity Heritage Library's Impact on Scientific
Research}. In: Library research showcase. Available from:
\url{http://hdl.handle.net/2142/95082}.

\leavevmode\vadjust pre{\hypertarget{ref-Urban2015}{}}%
Urban MC (2015) {Accelerating extinction risk from climate change}.
Science 348: 571--573. \url{https://doi.org/10.1126/science.aaa4984}

\leavevmode\vadjust pre{\hypertarget{ref-Wilkinson2016}{}}%
Wilkinson MD, Dumontier M, Aalbersberg IjJ, Appleton G, Axton M, Baak A,
Blomberg N, Boiten JW, da Silva Santos LB, Bourne PE, Bouwman J, Brookes
AJ, Clark T, Crosas M, Dillo I, Dumon O, Edmunds S, Evelo CT, Finkers R,
Gonzalez-Beltran A, Gray AJG, Groth P, Goble C, Grethe JS, Heringa J,
Hoen PAC t, Hooft R, Kuhn T, Kok R, Kok J, Lusher SJ, Martone ME, Mons
A, Packer AL, Persson B, Rocca-Serra P, Roos M, Schaik R van, Sansone
SA, Schultes E, Sengstag T, Slater T, Strawn G, Swertz MA, Thompson M,
Van Der Lei J, Van Mulligen E, Velterop J, Waagmeester A, Wittenburg P,
Wolstencroft K, Zhao J, Mons B (2016) {Comment: The FAIR Guiding
Principles for scientific data management and stewardship}. Scientific
Data 3: 1--9. \url{https://doi.org/10.1038/sdata.2016.18}

\leavevmode\vadjust pre{\hypertarget{ref-Wilson2007}{}}%
Wilson K, Bisby F (2007) {The Catalogue of Life: indexing the world's
species}. BGjournal 4: 24--29.

\end{CSLReferences}

\end{document}
